### 2016-04-08 ch02-qlogms/excitation-design.tex
Improve coupling figure

This results extends mutatis mutandis to systems consisting of more sub-systems.

\begin{figure}
\centering
\setlength\figurewidth{0.68\columnwidth}
\setlength\figureheight{0.68\figurewidth}
\input{\thisDir/figs/coupling.tikz}
\caption[Relative amplitudes of the off-diagonal blocks of the Fisher information matrix.]{The element with the largest absolute value in the off-diagonal blocks of the normalized information matrix for different dampings.
         The different plots are for different separations of the resonance frequencies, from 4\wdB to 64\wdB.
         The arrow indicates the direction of increasing separation.}
\label{fig:excitation:coupling}
\end{figure}

>>>>

This results extends \latin{mutatis mutandis} to systems consisting of more sub-systems.

\begin{figure}
\centering
\setlength\figurewidth{0.68\columnwidth}
\setlength\figureheight{0.68\figurewidth}
\input{\thisDir/figs/coupling.tikz}
\caption[Relative amplitudes of the off-diagonal blocks of the Fisher information matrix.]{The element with the largest absolute value in the off-diagonal blocks of the normalized information matrix for different dampings.
         The different plots are for different separations of the resonance frequencies, from $4\wdB$ to $64\wdB$.
         The arrow indicates the direction of increasing separation.}
\label{fig:excitation:coupling}
\end{figure}

### 2016-04-08 config/styles.inc.tex
Externalize some frequency grids
 - also computed alpha, delta for example grid.
Plots with grid summaries
Improve coupling figure

%TODO: avoid duplicated styles !!

@@

\pgfplotsset{gridline/.style={ycomb,solid,line width=0.7pt,mark size=1pt}}
\pgfplotsset{biggrid/.style={ycomb,solid,line width=1pt,mark size=1pt}}

@@

\pgfplotsset{connectline/.style={solid,line width=1.0pt}}
\pgfplotsset{linmsconnect/.style={color=linms,connectline,linmsmarker}}
\pgfplotsset{qlogmsconnect/.style={color=qlogms,connectline,qlogmsmarker}}
\pgfplotsset{clogmsconnect/.style={color=clogms,connectline,clogmsmarker}}
\pgfplotsset{plogmsconnect/.style={color=plogms,connectline,plogmsmarker}}

>>>>

% style to plot only every Nth point (1st, N+1st, ...)
% use as: `mark repeat=N`
% http://tex.stackexchange.com/questions/116690/pgfplots-marks-mandatory-for-1st-and-last-point
\pgfplotsset{
    mark repeat*/.style={
        scatter,
        scatter src=x,
        scatter/@pre marker code/.code={
            \pgfmathtruncatemacro\usemark{
                or(mod(\coordindex,#1)==0, (\coordindex==(\numcoords-1))
            }
            \ifnum\usemark=0
                \pgfplotsset{mark=none}
            \fi
        },
        scatter/@post marker code/.code={}
    }
}

@@

\pgfplotsset{gridline/.style={ycomb,solid,line width=0.7pt,mark size=1pt},line legend}
\pgfplotsset{biggrid/.style={ycomb,solid,line width=1pt,mark size=1pt}}

@@

\pgfplotsset{connectline/.style={solid,line width=1.0pt}}
\pgfplotsset{linmsconnect/.style={color=linms,connectline,linmsmarker}}
\pgfplotsset{logmsconnect/.style={color=logms,connectline,logmsmarker}}
\pgfplotsset{qlogmsconnect/.style={color=qlogms,connectline,qlogmsmarker}}
\pgfplotsset{clogmsconnect/.style={color=clogms,connectline,clogmsmarker}}
\pgfplotsset{plogmsconnect/.style={color=plogms,connectline,plogmsmarker}}
